Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-10 proposal/proposal.tex
Updated Overview section

The parking lots at the Colorado School of Mines (CSM, Mines) are often a source of frustration for students and faculty members. Because space on campus is limited, the lots are often unable to accommodate everyone who needs to use them. Students need to decide which lot to park in before they go to class; however, knowing which lots have free spaces usually requires driving through the lots looking for a space. The extra time spent searching one or many lots can make students or faculty late for class. If campus members could find out which lots had available spaces before they arrived, much time and frustration could be saved. The goal of this project is to design and deploy a working parking lot monitoring system that will be the first step towards a better parking experience on the Mines campus. The system will keep track of both the number of vehicles in a parking lot and the license plate numbers of those vehicles. The information will be available online to system administrators and Mines campus members. There are two main parts to this project:

@@

The goal of this project is to work with the ACMx group to deploy the system in two parking lots on campus, the CTLM upper lot and CTLM lower lot, which are the two closest parking lots to the CTLM building on the Mines campus. The system itself will consist of five main subsystems, which are described in detail in section 2.

@@

\section{Proposed Work}
\subsection{Overview}

>>>>

The parking lots at the Colorado School of Mines (CSM, Mines) can be a source of frustration for students and faculty members. Because space on campus is limited, the lots are often unable to accommodate everyone who needs to use them. Students need to decide which lot to park in before they go to class; however, knowing which lots have free spaces usually requires driving through the lots looking for a space. The extra time spent searching one or many lots can make students or faculty late for class. If campus members could find out which lots had available spaces before they arrived, much time and frustration could be saved. The goal of this project is to design and deploy a working parking lot monitoring system that will be the first step towards a better parking experience on the Mines campus. The system will keep track of both the number of vehicles in a parking lot and the license plate numbers of those vehicles. The information will be available online to system administrators and Mines campus members. There are two main parts to this project:

@@

The goal of this project is to work with the ACMx group to deploy the system in two parking lots on campus: the CTLM upper lot and CTLM lower lot, which are the two closest parking lots to the CTLM building on the Mines campus. The system itself will consist of five main subsystems, which are described in detail in section 2.

@@

\section{Proposed Work}
\subsection{Overview}
The project we are proposing will be an extension of the ACMx SmartLots project. We will collaborate closely with the ACMx group to create and deploy the first working parking lot monitoring system on the Mines campus. Our system will consist of several subsystems, each of which will be either an extension of a current ACMx subsystem or a new subsystem that will interface with the ACMx architecture. Figure 1 shows the overall architecture of our system, overlaid on a non-scaled map of the CTLM parking lots.

% Insert Image here. Is it OK for me to refer to it as 'figure 1' or should I change that part? Thanks for creating this graphic Santi!

The system will rely on three sensor nodes: one will be placed at the entrance to the upper lot, one at the entrance to the lower lot, and one at the junction between the two lots. Each sensor node will contain an Arduino Fio equipped with a tri-axial magnetometer that will be used to detect when a car passes the sensor. The work to determine the hardware configuration and software for the Fios has already been done by ACMx. Our contribution will be to also equip each node with a Raspberry Pi mini-computer and camera, which will take pictures of the license plates of cars as they pass by. When a car passes a sensor node, the magnetometer will detect the car, and the Fio will send an interrupt to the Pi via the XBEE radio, waking it up so it can take a picture of the license plate. There will be a central base station in an upper window of the CTLM building, which will receive all the data from the sensor nodes via transmission from the XBEE Pro radios attached to the sensor nodes. This base station Raspberry Pi will also have a camera attached that will take periodic images of the lots from above. These images will be used to reconcile the sensed data with the actual state of the lots. The base station will forward the data to the ACMx server, where it will be processed and displayed in the web application. The following sections describe the architecture and function of each of the aforementioned subsystems in detail.
